Complete OverView

### 2020-01-13 Study.Rmd
First Documentation

x3p_crosscut_optimize allows us to identify a cross section that is close to the heal of the bullet and does not suffer from defects(break-off, pitting, ... , etc)

>>>>

x3p_crosscut_optimize allows us to identify a cross section that is close to the heel of the bullet and does not suffer from defects(break-off, pitting, ... , etc)
